\chapter{Acknowledgement}
If there is one thing I know for sure about this thesis is that I could not have done it by myself. 
In particular, the support and encouragement from my supervisors Hui Tang, Anu Kaakinen and Frode Stordal, have been indispensable. Thank you so much!
Especially, I want to thank Anu for helping me out during my Covid disrupted exchange semester in Helsinki. I had a great time while it lasted. 
Moreover, I want to thank Christine Groot Zwaaftink at NILU for helping with solving the bias in FLEXDUST and Prof. Kazuo Osada at Nagoya University for providing data for model validation. The technical support team at MetOs also deserves praise, especially Anne Fouilloux, for helping with compiling FLEXPART on Saga. 

During the past two years, I have been lucky to share office with and become friends with an amazing bunch of fellow master students.
Among that bunch, there is one person that has meant a lot to me, Huiying Zhang. 
The walks, hikes, conversations and dinners we had together made all the difference during an otherwise stressful and isolating, seemingly never-ending pandemic. 


I also want to thank everyone who has helped me out throughout my studies at UiO and finding my place in Oslo. Especially Fysikkforeningen at UiO, which was like a home to me throughout my bachelor studies. Lillefy will always be close to my heart. I will also give a shoutout to Eirik Gallefoss for making the stress of the exams go away with a whiteboard marker and a thermos of coffee. 

Last but not least I want to thank my family for their everlasting support and for showing interest in my studies. 