\chapter*{Foreword}
Commonly the Foreword is written introduce the reader to the piece of work they are about to read, this Foreword on the other hand is primarily for the writer. The most important thing you have to bare in mind when you are writing a thesis is why are you writing this in the first place. This might sound like a trivial thing, but I promise you that there will not always be a flow of inspiration emanating out from the laptop every time you open this document. There will be times you would rather shove this piece of **@\#! document up someone bottom. At these moments I want you to scroll to the top and read this.

What is that makes science so special to you? Part of the answer lays in curiosity. Curiosity has always been one of your defining characteristics. All the way back to the time when you were 5 years old and wondered over why does some boats had a large bulge at the bow just below the surface, to in middle school when you discovered that emptiness constitutes most stuff you are surrounded by. Curiosity which brought you discovering dark matter, particle physics at Vitenfabrikken in your last year of High school. Convinced you to study physics at the University of Oslo after high school, and you would not listen to anything else. Even when you realised that particle physics wasn't your call in life after all, curiosity took hold of your hand introduced to fascinating world of meteorology. Where you learned about how fluffy clouds form and how they turn into mighty towering thunderclouds. How serious the consequences are if we continue our dependence on fossil fuels, and that if we want to avoid the most severe impacts we need to act now. Solving the climate crisis will be the issue of this century. \par Frode peaked your interest for dust, when he mentioned that he had a researcher looking at dust transport at Chinese Loess Plateau. Dust have always been there and surrounds us every day, yet we never pay it much attention except occasionally when vacuum cleaning and yet no matter how much we vacuum the dust always seems to return. Which makes you wonder, where does all this dust come from? That is the question that you have spent more than two years searching the answer to. Except that you have not been investigating your typical house hold dust, you have been looking for the origin of Chinese Loess, the oldest and thickest deposits of dust on Earth. In your quest to find the origin of the Chinese Loess have lead you in a wide variety... 

of the More or less at the same time you where reading about Lyra and marvellous quest to find the origin of the illusive dust particles, in the world of Philip Pullman's His Dark Materials. A story which in essence is about excitement of discovery, the value of friendship and the power of stubbornness.     